---
title: "Final project rubric"
format:
  gfm:
    toc: true
    toc-depth: 1
---



```{r}
#| message: false
#| echo: false
library(tidyverse)
library(gt)

writeup_rubric <- read_csv("write-up-final-project-rubric.csv")

pres_rubric <- 
	read_csv("presentation-final-project-rubric.csv")

get_rubric <- function(rubric_table, rubric_text) {
	rubric_table |> 
	filter(rubric == rubric_text) |> 
	pivot_wider(names_from = points, 
							values_from = text) |> 
	select(!rubric) |> 
	gt()
}


```


```{r}
mtcars |> 
	gt() |> 
	as_raw_html()
```



This document provides the rubric used to score the final project. 

# Presentation

The presentation is scored out of 15 points using the rubric below:

```{r}
#| echo: false

pres_rubric |> 
	filter(rubric %in% c("Content", "Overall style")) |> 
	pivot_wider(names_from = points, 
							values_from = text) |> 
	select(!rubric) |> 
	gt() |> 
	as_raw_html()


```


# Write-up

## Overview

The write-up is scored out of 25 points:


```{r}
#| echo: false

overall_scores <- 
tibble::tribble(
                         ~topic, ~points,
                 "Introduction",      3,
            "Code walk-through",      9,
                  "Conclusions",      3,
  "Resources for learning more",      1,
  "Resources you found helpful",      1,
                "Overall style",      8
  )

gt(overall_scores, rowname_col = "topic") |> 
	rows_add(topic = "Total", 
					 points = sum(overall_scores$points))
```

## Detailed rubric

The sections below provide the rubrics used to score each section of the write-up.

### Introduction (3 points)

```{r}
#| echo: false


get_rubric(writeup_rubric, "Introduction")


```

### **Code walk-through (9 points)**

```{r}
#| echo: false
get_rubric(writeup_rubric, "Code walk-through")

```

### Conclusions (3 points)

```{r}
#| echo: false
get_rubric(writeup_rubric, "Conclusions")
```

### Resources for learning more (1 point)

```{r}
#| echo: false
get_rubric(writeup_rubric, "Resources for learning more")
```

***Hallmarks of “needs more” feedback:*** This section felt underdeveloped. The student provided 1-2 resources but could have done more to offer ideas and resources for anyone who wants to learn more about their chosen topic.

### Resources you found helpful (1 point)

```{r}
#| echo: false
get_rubric(writeup_rubric, "Resources you found helpful")
```

***Hallmarks of “needs more” feedback:*** This section felt underdeveloped. The student provided 1-2 resources but could have done more to offer ideas and resources for anyone who wants to learn more about their chosen topic.

### Overall style (8 points)

```{r}
#| echo: false
get_rubric(writeup_rubric, "Overall style")
```

```{r}
#| echo: false
get_rubric(writeup_rubric, "Ease of access")
```
